### 2008-12-21 talk/ecoop2009/jitgen.tex
remove reference to year, as the cited paper is more recent

In 1971 Yoshihiko Futamura published a paper \cite{Futamura99} that proposed a
technique to automatically transform an interpreter of a programming language
into a compiler for the same language. This would solve the problem of having to
write a compiler instead of a much simpler interpreter. He proposed to use
partial evaluation to achieve this goal. He defined partial evaluation along the following lines:

>>>>

Yoshihiko Futamura published a paper \cite{Futamura99} that proposed a
technique to automatically transform an interpreter of a programming language
into a compiler for the same language. This would solve the problem of having to
write a compiler instead of a much simpler interpreter. He proposed to use
partial evaluation to achieve this goal. He defined partial evaluation along the following lines:
